Use Of Jigsaw Puzzle Solving Algorithms In The Real World

### 2024-04-13 LaTeX_paper/paper.tex
add unitn logo in paper start
use unitn margins

\documentclass{article}

% Required for inserting images
\usepackage{graphicx}

@@

% to set the margin of the page
\usepackage[a4paper, left=25mm,top=20mm,bottom=20mm,right=15mm]{geomet ry}

@@

\maketitle

>>>>

\documentclass[epsfig,a4paper,11pt,titlepage,twoside,openany]{article}
\usepackage{epsfig}
\usepackage{plain}
\usepackage{setspace}
\usepackage[paperheight=29.7cm,paperwidth=21cm,outer=1.5cm,inner=2.5cm,top=2cm,bottom=2cm]{geometry} % per definizione layout
\usepackage{titlesec} % per formato custom dei titoli dei capitoli

%\documentclass[epsfig,a4paper,11pt,titlepage,twoside,openany]{book}
% Required for inserting images
\usepackage{graphicx}

@@

@@

% \maketitle

\begin{center}

  \includegraphics[scale=1]{pictures/unitn_logo.pdf}

  \vspace{3 cm}

  \LARGE{Department of Information Engineering and Computer Science\\}

  \vspace{1 cm} 
  \Large{Bachelor’s Degree in\\
    Computer, Communications and Electronic Engineering
  }

  \vspace{2 cm} 
  \Large\textsc{Final Dissertation\\} 
  \vspace{1 cm} 
  \Huge\textsc{Title\\}
  \Large{\it{Use Of Jigsaw Puzzle Solving Algorithms In The Real World}}

  \vspace{2 cm} 
  \begin{tabular*}{\textwidth}{ c @{\extracolsep{\fill}} c }
  \Large{Supervisor} & \Large{Student}\\
  \Large{Patrignani Marco}& \Large{Sartore Luca}\\
  \end{tabular*}

  \vspace{2 cm}

  \Large{Academic year 2023/2024}

\end{center}
\newpage
